Supplementary Materials

### 2019-01-30 sup_mat/sup_mat.Rmd
a few changes to text and Fig 4

In total, particiapnts completed 160 trials in each session with the hetero- and homogenous side randomly varying from trial to trial.

## Adaptive Choice
For this task, participants viewed the display from approximately 47cm away, but no chin rest was used to ensure a constant viewing distance. The search display consisted of two target squares (one red and one blue), and 52 distractor squares: 12 red, 12 blue, 14 green, and 14 squares of variable colour, arranged in three rings around a fixation point. The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively). The participants' task was to find either a blue or a red square that contained a number between 2 and 5 inclusive. On every trial, just one blue and one red square contained a number between 2 and 5. Participants were instructed to find and report one of them. To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number inside. The distractor blue and red squares would always contain numbers between 6 and 9. The green squares contained numbers between 2 and 9. Participants were instructed to complete the task as quickly and as accurately as possible.

Before starting the task, participants were given 10 practice trials and were free to ask any questions before starting the main expriment. If a participant reported a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake. After the practice trials, they would then complete `r max(dat_ACS$Trial)` trials split into 4 equal length blocks (`r max(dat_ACS$Block_trial)` trials per block).

@@

## Foraging 
Viewing distance was approximately 47cm (no chin rest was used). At the beginning of each trial, participants were presented with 84 small shapes on the screen which subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively). Half of these were target items that participants were to click on, using the mouse cursor, until they had "collected" all of them (they disappeared when clicked). There were two types of search with this task. In feature search, participants were presented with circles of 4 different colours (red, blue, yellow, and green) and were instructed to click on all circles of two of the colours (e.g. click on the red and green, not the blue and yellow). In conjunction search, there were squares and circles coloured with two of the four possible colours, for example, they could be instructed to collect the blue squares and yellow circles, but to avoid the blue circles and yellow squares. In both conditions, if participants clicked on a non-target shape the trial immediately ended and re-started with 84 shapes in a new set of locations. Participants completed both of these conditions and the order was counterbalanced with the colours of the targets being randomised across participants.

Before starting the experiment, participants had 5 practice trials to familiarise themeselves with the task, after which they would begin 20 experimental trials. After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition. This took approximately 20 minutes.

@@

Data was collected from 64 Participants as originally planned. Four of these participants did not complete all parts of the experiment (either declining to participate in the second session, or could not be calibrated with the eye tracker), so four new participants were recruited to bring the total back up to `r num_participants`.

@@

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt_ACS_mean_acc <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ungroup() %>%
  mutate(mean_acc_ov = mean(Acc)) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc),
            mean_acc_ov = mean(mean_acc_ov)) %>%
  mutate(sd_acc = sd(mean_acc)) %>%
  filter(mean_acc > mean_acc_ov - 3*sd_acc) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt_ACS_mean_acc$labels$x <- "Participant"
plt_ACS_mean_acc$labels$y <- "Mean Accuracy"
# plt3

@@

```
A participant was excluded if their accuracy in the task was more than 3 standard deviations below the average for all participants. As can be seen in Figure \ref{fig:ACS_acc}, participants `r paste(excluded[1], "&", excluded[2])` were excluded for having an accuracy that was 3 standard deviations below the global average of `r round(avg_1, digits = 2)`.

@@

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_mean_acc
```
### Foraging
No participants were exlucded from the analysis of these data. However, participants 27, 40, 41, 42, and 43 were missing their data from the Feature search condition (Figure \ref{fig:For_switch_rt})

@@

## Data Processing
### Response Times 
Response Times in the Adaptive Choice and Split-Half tasks were normalised by applying a log2 transformation to the data as can be seen in Figure \ref{fig:ACS_SH_rt}. Also, response times that were 3 standard deviations from the mean were discarded.

>>>>

In total, particiapnts completed 160 trials in each session, with the hetero- and homogenous side randomly varying from trial to trial.

## Adaptive Choice
For this task, participants viewed the display from approximately 47cm away, but no chin rest was used to ensure a constant viewing distance. The search display consisted of two target squares (one red and one blue), and 52 distractor squares: 12 red, 12 blue, 14 green, and 14 squares of variable colour, arranged in three rings around a fixation point. The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively). The participants' task was to find either a blue or a red square that contained a number between 2 and 5 inclusive. On every trial, just one blue and one red square contained a number between 2 and 5. Participants were instructed to find and report one of them. To ensure we could tell which colour they found, the blue and red target squares would always have a different number inside. The distractor blue and red squares would always contain numbers between 6 and 9. The green squares contained numbers between 2 and 9. Participants were instructed to complete the task as quickly and as accurately as possible.

Before starting the task, participants were given 10 practice trials and were free to ask any questions before starting the main experiment. If a participant reported a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake. After the practice trials, they would then complete `r max(dat_ACS$Trial)` trials split into 4 equal length blocks (`r max(dat_ACS$Block_trial)` trials per block).

@@

## Foraging 
Viewing distance was approximately 47cm (no chin rest was used). At the beginning of each trial, participants were presented with 84 small shapes on the screen which subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively). Half of these were target items that participants were to click on, using the mouse cursor, until they had "collected" all of them (they disappeared when clicked). There were two types of search with this task. In feature search, participants were presented with circles of 4 different colours (red, blue, yellow, and green) and were instructed to click on all circles of two of the colours (e.g. click on the red and green, not the blue and yellow). In conjunction search, there were squares and circles coloured with two of the four possible colours, for example, they could be instructed to collect the blue squares and yellow circles, but to avoid the blue circles and yellow squares. In both conditions, if participants clicked on a non-target shape the trial immediately ended and re-started with 84 shapes in a new set of locations. Participants completed both of these conditions. Condition order was counterbalanced, and the colours of the targets was randomised across participants.

Before starting the experiment, participants completed five practice trials to familiarise themeselves with the task, after which they completed 20 experimental trials in each condition. This took approximately 20 minutes.

@@

Data were collected from 64 participants as originally planned. Four of these participants did not complete all parts of the experiment (either declining to participate in the second session, or could not be calibrated with the eye tracker), so four new participants were recruited to bring the total back up to `r num_participants`.

@@

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt_ACS_mean_acc <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ungroup() %>%
  mutate(mean_acc_ov = mean(Acc)) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc),
            mean_acc_ov = mean(mean_acc_ov)) %>%
  mutate(sd_acc = sd(mean_acc)) %>%
  # filter(mean_acc > mean_acc_ov - 3*sd_acc) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt_ACS_mean_acc$labels$x <- "Participant"
plt_ACS_mean_acc$labels$y <- "Mean Accuracy"
# plt3

@@

```
We excluded any participant with accuracy more than 3 standard deviations below the average for all participants. As can be seen in Figure \ref{fig:ACS_acc}, participants `r paste(excluded[1], "&", excluded[2])` were excluded for having an accuracy that was 3 standard deviations below the global average of `r round(avg_1, digits = 2)`.

@@

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_mean_acc
```
### Foraging
No participants were excluded for poor performance on the foraging task. However, participant 27 and participants 40 to 43 were missing their data from the feature search condition (Figure \ref{fig:For_switch_rt}). We had not planned to use the results from the feature search condition in the correlation calculations, so these participants were not excluded.

@@

## Data Processing
### Response Times 
Response Times in the Adaptive Choice and Split-Half tasks were skewed, as can be seen in Figure \ref{fig:ACS_SH_rt}. We therefore normalised the data by applying a log2 transformation. Response times that were 3 standard deviations from the mean were discarded.
